Make any stupid plot you want

### 2021-05-05 draft/sections/intro.tex
closing out fig redos + labeling + consistently precip
cleaned up figures/new figures

\subsection{Structure:}
\label{sec:intro:structure}

@@

\subsection{Tools}
\label{sec:intro:data:tools}

\begin{figure}[H]
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=1\textwidth]{figures/intro/table.png}
        \caption{}
        \label{fig:intro:table}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=1\textwidth]{figures/intro/landsat.png}
        \caption{}
        \label{fig:intro:image}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=1\textwidth]{figures/math/graph.png}
        \caption{}
        \label{fig:intro:graph}
    \end{subfigure}
    \caption{Visualization libraries, especially ones tied to specific domains, tend to be architectured around a core data structure, such as tables \autoref{fig:intro:table}, images \autoref{fig:intro:image}, or networks \autoref{fig:intro:graph}.
    %%revise as combined fig?
    }
    \label{fig:intro:data}
\end{figure}

@@

\subsection{Data}
\label{sec:intro_data}
Fiber bundles were proposed by Butler as a core data structure for visualization because they encode data \textit{continuity} separately from the components of the dataset\cite{butlerVisualizationModelBased1989,butlerVectorBundleClassesForm1992}. Butler's model lacks a robust way of describing variables; therefore we encode a schema like description of the data in the fiber bundle using Spivak's topological description of data types \cite{spivakDatabasesAreCategories2010,spivakSIMPLICIALDATABASES}. In this work, we refer to the points of the dataset as \textit{records}, as defined by Spivak. Each \textit{component} of the record is a single object, such as a precipitation measurement, a station name, or an image. We generalize \textit{component} to mean all objects in the dataset of a given type, such as all precipitation values or station names or images. The way in which these records are connected is the \textit{continuity} or more generally topology.

>>>>

\subsection{Structure Visualizations Preserve}
\label{sec:intro:structure}

@@

\subsection{Tools}
\label{sec:intro:data:tools}
\begin{figure}[H]
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=1\textwidth]{figures/intro/table.png}
        \caption{}
        \label{fig:intro:table}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=1\textwidth]{figures/intro/landsat.png}
        \caption{}
        \label{fig:intro:image}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=1\textwidth]{figures/math/graph.png}
        \caption{}
        \label{fig:intro:graph}
    \end{subfigure}
    \caption{Visualization libraries, especially ones tied to specific domains, tend to be architectured around a core data structure, such as tables \autoref{fig:intro:table}, images \autoref{fig:intro:image}, or networks \autoref{fig:intro:graph}.
    %%revise as combined fig?
    }
    \label{fig:intro:data}
\end{figure}

@@

\subsection{Data}
\label{sec:intro:data:continuity}
Fiber bundles were proposed by Butler as a core data structure for visualization because they encode data \textit{continuity} separately from the components of the dataset\cite{butlerVisualizationModelBased1989,butlerVectorBundleClassesForm1992}. Butler's model lacks a robust way of describing variables; therefore we encode a schema like description of the data in the fiber bundle using Spivak's topological description of data types \cite{spivakDatabasesAreCategories2010,spivakSIMPLICIALDATABASES}. In this work, we refer to the points of the dataset as \textit{records}, as defined by Spivak. Each \textit{component} of the record is a single object, such as a precipitation measurement, a station name, or an image. We generalize \textit{component} to mean all objects in the dataset of a given type, such as all precipitation values or station names or images. The way in which these records are connected is the \textit{continuity} or more generally topology.

### 2021-05-05 draft/sections/math.tex
implementation section
cleaned up figures/new figures

\section{Topological Equivariant Artist Model}
\label{sec:math}
To guide the implementation of structure preserving building block components, we develop a mathematical formalism of visualization that specifies how these components preserve \textit{continuity} and \textit{equivariance}. Inspired by the somewhat analogous component in Matplotlib\cite{hunterArchitectureOpenSource}, we call the transformation from data space to graphic that these building block components implement the \textit{artist}.
\begin{equation}
    \label{eq:artist}
    \mathscr{\vartist}: \mathscr{\dtotal} \rightarrow \mathscr{\gtotal}
\end{equation}
The \textit{artist} $\mathscr{\vartist}$ is a map from the data $\mathscr{\dtotal}$ to graphic $\mathscr{\gtotal}$ fiber bundles. To explain how the \textit{artist} is a structure preserving map from data to graphic, we first describe how we model data (\autoref{sec:math:data}) and graphics (\autoref{sec:math:graphic}) as topological structures that encapsulate component types and continuity. We then discuss the maps from graphic to data (\autoref{sec:math:graphic:base}, data components to visual components (\autoref{sec:math:artist:nu}), and visual components into graphic (\autoref{sec:math:artist:q}) that make up the artist.

\subsection{Data Space \dtotal}
\label{sec:math:data}
Building on Butler's proposal of using fiber bundles as a common data representation structure for visualization data\cite{butlerVectorBundleClassesForm1992, butlerVisualizationModelBased1989}, a fiber bundle is a tuple $(\dtotal,\,\dbase,\,\pi ,\,\dfiber)$ defined by the projection map $\pi$
\begin{equation}
    \label{eq:fiber_bundle}
    \begin{tikzcd}
        \dfiber \arrow[r, hook] & \dtotal \arrow[r, "\pi"] & \dbase
    \end{tikzcd}
\end{equation}
that binds the components of the data in \dfiber\ to the continuity of the data encoded in \dbase. The fiber bundle models the properties of data component types \dfiber\ (\autoref{sec:math:data:fiber}), the continuity of records \dbase\ (\autoref{sec:math:data:base}), the collections of records \dsection\ (\autoref{sec:math:data:section}), and the space \dtotal\ of all possible datasets with these components and continuity. By definition fiber bundles are locally trivial\cite{spanier1989algebraic,LocallyTrivialFibre}, meaning that over a localized neighborhood $U$ the total space is the cartesian product $\dbase\times\dfiber$. We use fiber bundles as the data model because they are inclusive enough to express all the types of structures of data described in \autoref{sec:intro:data:tools}

\subsubsection{Variables in Fiber Space \dfiber}
\label{sec:math:data:fiber}
To formalize the structure of the data components, we use notation introduced by Spivak \cite{spivakSIMPLICIALDATABASES} that binds the components of the fiber to variable names. This allows us to describe the components in a schema like way. Spivak constructs a set \ftotal\ that is the disjoint union of all possible objects of types $\{\ftype_0, \ldots, \ftype_m\} \in \ftypes$, where \ftypes\ are the data types of the variables in the dataset. He then defines the single variable set \fttype\ 
\begin{equation}
    \label{eq:data_types}
    \begin{tikzcd}
        \fttype \arrow[r] \arrow[d, "\pi_{\fsection}"'] & \ftotal \arrow[d, "\pi"] \\
        \fnames \arrow[r, "\fsection"']                          & \ftypes       
    \end{tikzcd}
\end{equation}
which is \ftotal\ restricted to objects of type \ftype\ bound to variable name \fname. The \fttype\ lookup is by name to specify that every component is distinct, since multiple components can have the same type \ftype. Given \fsection, the fiber for a one variable dataset is
\begin{equation}
    \dfiber = \ftotal_{\fsection(\fname)} = \ftotal_{\ftype} 
\end{equation}
where \fsection\ is the schema that binds a variable name \fname\ to its datatype \ftype. A dataset with multiple components has a fiber that is the cartesian cross product of $\ftotal_{\fsection}$ applied to all the columns:
\begin{equation}
F = \ftotal_{\fsection(\fname_{1})}\times \ldots \ftotal_{\fsection(\fname_{i})} \ldots\times \ftotal_{\fsection(\fname_{n})}
\end{equation}
which can also be written as 
\begin{equation}
    \label{eq:math:data:fiber:decompose}
    \dfiber= \dfiber_{0} \times \ldots \times \dfiber_{i}\times\ldots\times \dfiber_{n}
\end{equation}
which allows us to decouple \dfiber\ into components $\dfiber_i = \ftotal_{\fsection{(\fname_{i})}}$.

\begin{figure}[H]
    \includegraphics[width=1\textwidth]{figures/math/fiber.png}
    \caption{The fiber space is the set of all combinations of all theoretically possible values of the components.  The 2D fiber \(\dfiber=\reals\times\realsp\) (a) encodes the properties of \textit{time} and \textit{precipitation} components.  One dimension of the fiber encodes the range of possible values for the time component of the dataset, which is a subset of the \reals, while the other dimension encodes the range of possible values  \realsp\ for the precipitation component. This means the fiber is the set of points \textit{(precipitation, time)} that are all the combinations of \textit{precipitation} $\times$ \textit{time}. The 3D fiber (b) encodes points at all possible combinations of \textit{precipitation}, \textit{latitude}, and \textit{longitude}.}
    \label{fig:math:data:fiber}
\end{figure}

For example, the records in the 2D fiber (a) in \autoref{fig:math:data:fiber} are a pair of \textit{times} and \textdegree K \textit{precipitation} measurements taken at those times. Time is a positive number of type \texttt{datetime} which can be resolved to floats $\ftotal_{\texttt{datetime}}= \reals$. Temperature values are real positive numbers $\ftotal_{\texttt{float}} = \realsp$. The fiber is 
\begin{equation*}
    \dfiber =  \reals \times \realsp 
\end{equation*} 
where the first component $F_0$ is the set of values specified by $(\fname=time,\, \ftype=\texttt{datetime},\, \fttype=\reals)$ and $F_1$ is specified by $(\fname=precipitation,\, \ftype=\texttt{float},\, \fttype=\reals)$ and is the set of values $\fttype=\reals$. In the 3D fiber (b) in \autoref{fig:math:data:fiber}, time is replaced with location. This location variable is of type \texttt{point} and has two components \textit{latitude} and \textit{longitude} $\{(lat,lon) \in \reals^{2} \mid  -90\leq lat \leq 90,\, 0 \leq lon \leq 360\}$. The fiber for this dataset is
\begin{equation*}
    \dfiber = \reals \times [0, 360] \times [-90, 90]
\end{equation*} 
where the dimensionality of the fiber does not change, but the components of the fiber can be coupled. For example, \textit{location} can can either be specified as \((\fname = location,\, \ftype = \texttt{point},\, \fttype=\reals^{2})\)or \((\fname=latitude,\, \ftype=\texttt{float}, \, \fttype=\reals)\) and \((\fname=longitude,\, \ftype=\texttt{float},\,\fttype=\reals)\).

@@

\subsubsection{Data \dsection}
\label{sec:data_section}
While the projection function $\pi:\dtotal \rightarrow\dbase$ ties together the base space \dbase\ with the fiber \dfiber, a section $\dsection: \dbase\rightarrow \dtotal$ encodes a dataset. A section function takes as input location $\dbasepoint \in \dbase$ and returns a record $\delement \in \dtotal$. For example, in the special case of a table \cite{spivakSIMPLICIALDATABASES}, \dbase\ is a set of row ids, \dfiber\ is the columns, and the section \dsection\ returns the record \delement\ at a given key in \dbase. For any fiber bundle, there exists a map
\begin{equation}
    \begin{tikzcd}
        \dfiber \arrow[r, hook] & \dtotal \arrow[d, "\pi"'] \\
                          & \dbase \arrow[u, "\dsection"', bend right]
    \end{tikzcd}
\end{equation}
 such that $\pi(\dsection(\dbasepoint)) = \dbasepoint$. The set of all global sections is denoted as $\Gamma(\dtotal)$. Assuming a trivial fiber bundle $\dtotal = \dbase \times \dfiber$, the section is 
\begin{equation}
    \label{eq:section_return}
    \dsection(\dbasepoint) = (\dbasepoint, (g_{\dfiber_{0}}(\dbasepoint), \ldots, g_{\dfiber_{n}}(\dbasepoint)))
\end{equation}
where $g: \dbase \rightarrow \dfiber$ is the index function into the fiber. This formulation of the section also holds on locally trivial sections of a non-trivial fiber bundle. Because we can decompose the bundle and the fiber (\autoref{eq:math:data:base:decompose}, \autoref{eq:math:data:fiber:decompose}), we can decompose \dsection\ as 
\begin{equation}
\label{eq:math:data:section:decompose}
\dsection= (\dsection_0,\ldots, \dsection_i, \dots, \dsection_n) 
\end{equation}
where each section $\dsection_i$ maps into a record on a component $\dfiber_i \in \dfiber$. This allows for accessing the data component wise in addition to accessing the data in terms of its location over \dbase.

@@

\subsubsection{Equivalance class of artists $\vartist^{\prime}$}
\label{sec:artist_equivalance}
\begin{figure}[H]
    \includegraphics[width=1\textwidth]{figures/math/equivalent_artists.png}
   \caption{Each scatter plot is generated via a unique artist function $\vartist_{i}$, but they only differ in aesthetic styling. Therefore, these artists are all members of an equivalence class $\vartist_{i} \in \vartist{\prime}$}
    \label{fig:math:artist:equivalence}
\end{figure}
Representational invariance, as defined by Kindlmann and Scheidegger, is the notion that visualizations are equivalent if changing the visual representation, such as colors or shapes, does not change the meaning of the visualization\cite{kindlmannAlgebraicProcessVisualization2014}. We propose that visualizations are invariant if they are generated by artists that are members of an equivalence class 
\begin{equation*}
\{\vartist \in \vartist^{\prime}: \vartist_{1} \equiv \vartist_{2}\}
\end{equation*}
For example, every scatter plot in \autoref{fig:math:artist:equivalence} is a scatter of the same datasets mapped to the \textit{x position} and \textit{y position} in the same way. The scatter plots only differ in the choice of constant visual literals, differing in color and marker shape. Each scatter is generated by an artist $\vartist_{i}$, and every scatter is generated by a member of the equivalence class $\vartist_{i} \in \vartist{\prime}$. Since it is impractical to implement a new artist for every single graphic, the equivalance class provides a way to evaluate an implementation of a generalized artist. Given equivalent, but no necessarily identical, \vchannel, \vmark, and \vindex, two artists are equivalent. This criteria also allows for comparing artists across libraries. 
\end{document}

>>>>

\section{Topological Equivariant Artist Model}
\label{sec:math}
To guide the implementation of structure preserving visualization components, we develop a mathematical formalism of visualization that specifies how these components preserve \textit{continuity} and \textit{equivariance}. Inspired by the analogous classes in Matplotlib\cite{hunterArchitectureOpenSource}, we call the transformation from data space to graphic space that these building block components implement the \textit{artist}.
\begin{equation}
    \label{eq:artist}
    \mathscr{\vartist}: \mathscr{\dtotal} \rightarrow \mathscr{\gtotal}
\end{equation}
The \textit{artist} $\mathscr{\vartist}$ is a map from data $\mathscr{\dtotal}$ to graphic $\mathscr{\gtotal}$ fiber bundles. To explain how the \textit{artist} is a structure preserving map from data to graphic, we first model data (\autoref{sec:math:data}) and graphics (\autoref{sec:math:graphic}) as topological structures that encapsulate component types and continuity. We then discuss the funtional maps from graphic to data (\autoref{sec:math:graphic:base}), data components to visual components (\autoref{sec:math:artist:nu}), and visual components into graphic (\autoref{sec:math:artist:q}) that make up the artist.

\subsection{Data Space \dtotal}
\label{sec:math:data}
We use fiber bundles as the data model because they are inclusive enough to express all the types of structures of data described in \autoref{sec:intro:data:tools}. A fiber bundle is a tuple $(\dtotal,\,\dbase,\,\pi ,\,\dfiber)$ defined by the projection map $\pi$
\begin{equation}
    \label{eq:fiber_bundle}
    \begin{tikzcd}
        \dfiber \arrow[r, hook] & \dtotal \arrow[r, "\pi"] & \dbase
    \end{tikzcd}
\end{equation}
that binds the components of the data in \dfiber\ to the continuity of the data encoded in \dbase. Our use of fiber bundles builds on Butler's work proposing that fiber bundles should be the common data abstraction for visualization data\cite{butlerVectorBundleClassesForm1992, butlerVisualizationModelBased1989}. The fiber bundle models the properties of data component types \dfiber\ (\autoref{sec:math:data:fiber}), the continuity of records \dbase\ (\autoref{sec:math:data:base}), the collections of records (\autoref{sec:math:data:section}), and the space \dtotal\ of all possible datasets with these components and continuity. By definition fiber bundles are locally trivial\cite{spanier1989algebraic,LocallyTrivialFibre}, meaning that over a localized neighborhood $U$ the total space is the cartesian product $\dbase\times\dfiber$.

\subsubsection{Variables in Fiber Space \dfiber}
\label{sec:math:data:fiber}
To formalize the structure of the data components, we use Spivak's description of the schema \cite{spivakSIMPLICIALDATABASES} as a fiber bundle to bind the components of the fiber to variable names and data types. Spivak constructs a set \ftotal\ that is the disjoint union of all possible objects of types $\{\ftype_0, \ldots, \ftype_m\} \in \ftypes$, where \ftypes\ are the data types of the variables in the dataset. He then defines the single variable set \fttype\ 
\begin{equation}
    \label{eq:data_types}
    \begin{tikzcd}
        \fttype \arrow[r] \arrow[d, "\pi_{\fsection}"'] & \ftotal \arrow[d, "\pi"] \\
        \fnames \arrow[r, "\fsection"']                          & \ftypes       
    \end{tikzcd}
\end{equation}
which is \ftotal\ restricted to objects of type \ftype\ bound to variable name \fname. The \fttype\ lookup is by name to specify that every component is distinct, since multiple components can have the same type \ftype. Given \fsection, the fiber for a one variable dataset is
\begin{equation}
    \dfiber = \ftotal_{\fsection(\fname)} = \ftotal_{\ftype} 
\end{equation}
where \fsection\ is the schema that binds a variable name \fname\ to its datatype \ftype. A dataset with multiple components has a fiber that is the cartesian cross product of $\ftotal_{\fsection}$ applied to all the columns:
\begin{equation}
F = \ftotal_{\fsection(\fname_{1})}\times \ldots \ftotal_{\fsection(\fname_{i})} \ldots\times \ftotal_{\fsection(\fname_{n})}
\end{equation}
which can also be written as 
\begin{equation}
    \label{eq:math:data:fiber:decompose}
    \dfiber= \dfiber_{0} \times \ldots \times \dfiber_{i}\times\ldots\times \dfiber_{n}
\end{equation}
which allows us to decouple \dfiber\ into components $\dfiber_i = \ftotal_{\fsection{(\fname_{i})}}$.

\begin{figure}[H]
    \includegraphics[width=1\textwidth]{figures/math/fiber.png}
    \caption{The fiber space is the cartesian product of the components.  The 2D fiber \(\dfiber=\reals\times\realsp\) (a) encodes the properties of \textit{time} and \textit{precipitation} components.  One dimension of the fiber encodes the range of possible values for the time component of the dataset, which is a subset of the \reals, while the other dimension encodes the range of possible values  \realsp\ for the precipitation component. This means the fiber is the set of points \textit{(precipitation, time)} that are all the combinations of \textit{precipitation} $\times$ \textit{time}. The 3D fiber (b) encodes points at all possible combinations of \textit{precipitation}, \textit{latitude}, and \textit{longitude}.}
    \label{fig:math:data:fiber}
\end{figure}

For example, the records in the 2D fiber (a) in \autoref{fig:math:data:fiber} are a pair of \textit{times} and \textit{precipitation} measurements taken at those times. Time is a positive number of type \texttt{datetime} which can be resolved to $\ftotal_{\texttt{datetime}}= \reals$. Precipitation values are real positive numbers $\ftotal_{\texttt{float}} = \realsp$. The fiber is 
\begin{equation*}
    \dfiber =  \reals \times \realsp 
\end{equation*} 
where the first component $F_0$ is the set of values specified by $(\fname=time,\, \ftype=\texttt{datetime},\, \fttype=\reals)$ and $F_1$ is specified by $(\fname=precipitation,\, \ftype=\texttt{float},\, \fttype=\reals)$ and is the set of values $\fttype=\reals$. In the 3D fiber (b) in \autoref{fig:math:data:fiber}, time is replaced with location. This location variable is of type \texttt{point} and has two components \textit{latitude} and \textit{longitude} $\{(lat,lon) \in \reals^{2} \mid  -90\leq lat \leq 90,\, 0 \leq lon \leq 360\}$. The fiber for this dataset is
\begin{equation*}
    \dfiber = \reals \times [0, 360] \times [-90, 90]
\end{equation*} 
and can either be thought of as having two components  
\begin{equation}
    \{(\fname=precipitation,\, \ftype=\texttt{float},\, \fttype=\reals), ((\fname = location,\, \ftype = \texttt{point},\, \fttype=\reals^{2})\}
\end{equation}
 or three
 \begin{equation}
    \{(\fname=precipitation,\, \ftype=\texttt{float},\, \fttype=\reals), (\fname=latitude,\, \ftype=\texttt{float}, \, \fttype=\reals), (\fname=longitude,\, \ftype=\texttt{float},\,\fttype=\reals)\}
 \end{equation}

@@

\subsubsection{Data \dsection}
\label{sec:math:data:section}
While the projection function $\pi:\dtotal \rightarrow\dbase$ ties together the base space \dbase\ with the fiber \dfiber, a section $\dsection: \dbase\rightarrow \dtotal$ encodes a dataset. A section function takes as input location $\dbasepoint \in \dbase$ and returns a record $\delement \in \dtotal$. For example, in the special case of a table \cite{spivakSIMPLICIALDATABASES}, \dbase\ is a set of row ids, \dfiber\ is the columns, and the section \dsection\ returns the record \delement\ at a given key in \dbase. For any fiber bundle, there exists a map
\begin{equation}
    \begin{tikzcd}
        \dfiber \arrow[r, hook] & \dtotal \arrow[d, "\pi"'] \\
                          & \dbase \arrow[u, "\dsection"', bend right]
    \end{tikzcd}
\end{equation}
 such that $\pi(\dsection(\dbasepoint)) = \dbasepoint$. The set of all global sections is denoted as $\Gamma(\dtotal)$. Assuming a trivial fiber bundle $\dtotal = \dbase \times \dfiber$, the section is 
\begin{equation}
    \label{eq:section_return}
    \dsection(\dbasepoint) = (\dbasepoint, (g_{\dfiber_{0}}(\dbasepoint), \ldots, g_{\dfiber_{n}}(\dbasepoint)))
\end{equation}
where $g: \dbase \rightarrow \dfiber$ is the index function into the fiber. This formulation of the section also holds on locally trivial sections of a non-trivial fiber bundle. Because we can decompose the bundle and the fiber (\autoref{eq:math:data:base:decompose}, \autoref{eq:math:data:fiber:decompose}), we can decompose \dsection\ as 
\begin{equation}
\label{eq:math:data:section:decompose}
\dsection= (\dsection_0,\ldots, \dsection_i, \dots, \dsection_n) 
\end{equation}
where each section $\dsection_i$ maps into a record on a component $\dfiber_i \in \dfiber$. This allows for accessing the data component wise in addition to accessing the data in terms of its location over \dbase.

@@

\subsubsection{Equivalance class of artists $\vartist^{\prime}$}
\label{sec:artist_equivalance}
\begin{figure}[H]
    \includegraphics[width=1\textwidth]{figures/math/equivalent_artists.png}
   \caption{Each scatter plot is generated via a unique artist function $\vartist_{i}$, but they only differ in aesthetic styling. Therefore, these artists are all members of an equivalence class $\vartist_{i} \in \vartist{\prime}$}
    \label{fig:math:artist:equivalence}
\end{figure}
Representational invariance, as defined by Kindlmann and Scheidegger, is the notion that visualizations are equivalent if changing the visual representation, such as colors or shapes, does not change the meaning of the visualization\cite{kindlmannAlgebraicProcessVisualization2014}. We propose that visualizations are invariant if they are generated by artists that are members of an equivalence class 
\begin{equation*}
\{\vartist \in \vartist^{\prime}: \vartist_{1} \equiv \vartist_{2}\}
\label{eq:math:artist:aprime}
\end{equation*}
For example, every scatter plot in \autoref{fig:math:artist:equivalence} is a scatter of the same datasets mapped to the \textit{x position} and \textit{y position} in the same way. The scatter plots only differ in the choice of constant visual literals, differing in color and marker shape. Each scatter is generated by an artist $\vartist_{i}$, and every scatter is generated by a member of the equivalence class $\vartist_{i} \in \vartist{\prime}$. Since it is impractical to implement a new artist for every single graphic, the equivalance class provides a way to evaluate an implementation of a generalized artist. Given equivalent, but no necessarily identical, \vchannel, \vmark, and \vindex, two artists are equivalent. This criteria also allows for comparing artists across libraries. 
\end{document}

### 2021-05-05 draft/sections/next.tex
cleaned up figures/new figures

While TEAM specifies the components, the developers building libraries using TEAM components decide which compositions of components are semantically correct for the domain. For this reason, TEAM does not include data space transforms, as are incorporated into libraries like Tableau or ggplot, instead leaving choice of computations to implementors of the data object. TEAM's intentional ignorance of semantics also means it cannot evaluate whether a figurative glyph \cite{byrneAcquiredCodesMeaning2016} is a semantically correct choice, but it can enforce equivariance constraints of glyphs generated from data components enforcing equivariance of figurative glyphs \cite{byrneAcquiredCodesMeaning2016} generated from data components\cite{beckfeathers2014,byrneFigurativeFramesCritical2017}. TEAM also allows to graphics to have a lower dimensional continuity than the source data when a retraction map from one continuity to the other exists. For example, TEAM components could transform 1D continuous data into 0D discrete graphics, e.g. bar charts or scatter plots. As with computations, it is the role of the domain specific library to determine which figurative glyphs and continuity downgrades are appropriate.

>>>>

While TEAM specifies the components, the developers building libraries using TEAM components decide which compositions of components are semantically correct for the domain. For this reason, TEAM does not include data space transforms, as are incorporated into libraries like Tableau or ggplot, instead leaving choice of computations to implementors of the data object. TEAM's intentional ignorance of semantics also means it cannot evaluate whether a figurative glyph \cite{byrneAcquiredCodesMeaning2016} is a semantically correct choice, but it can enforce equivariance constraints of glyphs generated from data components enforcing equivariance of figurative glyphs \cite{byrneAcquiredCodesMeaning2016} generated from data components\cite{beckfeathers2014,byrneFigurativeFramesCritical2017}. TEAM also allows graphics to have a lower dimensional continuity than the source data when a retraction map from one continuity to the other exists. For example, TEAM components could transform 1D continuous segments into 0D discrete elements, e.g. bar charts or scatter plots. As with computations, it is the role of the domain specific library to determine which figurative glyphs and continuity downgrades are appropriate.
